\chapter{Abstract}
% OPTIONAL SOLUTION: Use these settings if you are writing a monograph and have
% only one abstract. Do not use them if you have an abstract at the beginning of
% each chapter/paper.

\abstractintoc{} % Add abstract to Table of Contents
% \abstractnum % Format abstract like a chapter

% \begin{abstract}

TODO - This is too vague for an abstract. Be more academic here. Do popolar
science in the introduction.

This thesis is focused on robust motion planning for a nonlinear system model.
Planning with uncertainty is necessary in order for an algorithm to move out of
the lab and into the real world as in reality there are always uncertainty in
planning. Knowledge of position, the environment and the dynamics of the system
are all uncertain to some degree. Sensory noise, tuning and readings may be off.
Limited precision, and accidents may hinder the measurements and leave them with
a an error term. Thus in order for a planner to give guarantees on safe
traversal through a real world environment, a motion planner needs to handle
uncertainties.

The \rrtfunnel{} algorithm is the answer provided to handle a subset of these
problems. As it currently stands the algorithm handles uncertainty only in the
position of the dynamical system, but can be easily extended to handle
uncertainty in input and speed as well. Handling uncertainties in the
environment is currently not handled.

The algorithm is built up through two main parts. One is the calculation of
\textit{robust motion primitives}, which allows the global motion planner (in
essence a regular \ac{RRT} algorithm) to remain completely oblivious to these
difficulties, and hence act as though there were no uncertainties during the
planning stage. This means that a lot of the difficulty of planning is handled
during the off-line phase of generating the robust motion primitives themselves.
This is done through the theory of \ac{SOS} programming and verification.
Through formulating the search for a \textit{Lyapunov function} for the system
as a \ac{SOS} program, the trajectories are extended to so called `funnels',
which incorporate all the states the system can be in during a given time frame
-- even in the face of uncertainties. In the literature this is referred to as a
\textit{finite time reachable set}, meaning that if the calculations are
correct, it contains all the states that the system can evolve to given a set of
initial conditions and a bounded uncertainty term.

Later the aforementioned funnels are employed as \textit{motion primitives} for
the global motion planning algorithm. Which means that they all encode a
discrete action. For the dynamical system in this thesis, which is a simple
unicycle model, this means that the motion primitives can be as simple
`turn-left', `turn-right', or `go-straight' -- yet a basis set should have a few
more primitives. Thus by stacking one motion primitive after the other, one is
able to create a plan, and hence build one long motion primitive through the
overarching environment. With the motion primitives being robust to uncertainty,
these plans are in theory guaranteed to be collision-free. The reason the theory
employed here does not necessarily apply to the real world is that most noise is
not bounded in the real world, and hence may break our basic assumption that it
is.

This theoretical robustness guarantee is later put to the test in simulated
experimental runs through a strip of forest of some density meant to make
planning difficult, along with a cross-wind as the system noise. Hence the
airplane is constantly faced with a positional offset, and is forced to deal
with this as best as it is able to during execution of the plan. As is shown,
the robustness guarantees provided by the Lyapunov functions found through the
\ac{SOS} programs formulated do provide safe traversal through the environment,
as opposed to a planner which does not.

% \end{abstract}
