\chapter{Acknowledgments}

\paragraph{} I would like to acknowledge, and thank Dr. Majumdar for his kind help when I
have been stuck, and for his code stubs which provided the basis for the
implementation of this thesis, and for which I probably not would have gotten
far.

\paragraph{A} thanks also goes out to Prof. Russ Tedrake, who, even though his time was
limited found the time for guidance, and thoughtful insights.

\paragraph{Many} thanks to my supervisors, Marius Thoresen and Kim Mathiassen, who have read
through the thesis many times, and helped polish the initial rubble into the
work which lays in front of you today. Now you be the judge.

\paragraph{Strangest} part of the last eighteen months is that, even though I was a stranger
to motion planning -- all humble and ready to learn, I now probably have more
unanswered questions than I had before. Motion planning is a huge scientific
research area, spanning vast topics such as robotics to mathematical optimization
and computer science. All in which are beyond the scope of a single human being.

\paragraph{A} thanks to all my friends (you know who you are), who have waited patiently for
me to join the ranks of adulthood, while all along having kept me from social
and economical ruin these past two years.

\paragraph{And} lastly, I would like to thank my dedicated and caring parents (my
step-parents also) for making me who I am today -- even though their efforts has
not gone unhindered.

Thank you!
